### 2025-03-21 CV2/papers.tex
update papers

@@

@@

\textbf{\href{https://proceedings.neurips.cc/paper/2019/hash/6a8018b3a00b69c008601b8becae392b-Abstract.html}{Stochastic proximal langevin algorithm: Potential splitting and nonasymptotic rates}} (Adil Salim, Dmitry Kovalev, Peter Richtarik). \textit{Advances in Neural Information Processing Systems}, 2019.

@@

@@

\textbf{\href{https://arxiv.org/abs/2407.02020}{Decentralized Optimization with Coupled Constraints}} (Demyan Yarmoshik, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov, Dmitry Kovalev). \textit{arXiv preprint arXiv:2407.02020}, 2024.
\textbf{\href{https://arxiv.org/abs/2405.18031}{Lower Bounds and Optimal Algorithms for Non-Smooth Convex Decentralized Optimization over Time-Varying Networks}} (Dmitry Kovalev, Ekaterina Borodich, Alexander Gasnikov, Dmitrii Feoktistov). \textit{arXiv preprint arXiv:2405.18031}, 2024.

>>>>

\textbf{\href{https://arxiv.org/abs/2407.02020}{Decentralized Optimization with Coupled Constraints}} (Demyan Yarmoshik, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov, Dmitry Kovalev). \textit{International Conference on Learning Representations}, 2025.
\textbf{\href{https://arxiv.org/abs/2405.18031}{Lower Bounds and Optimal Algorithms for Non-Smooth Convex Decentralized Optimization over Time-Varying Networks}} (Dmitry Kovalev, Ekaterina Borodich, Alexander Gasnikov, Dmitrii Feoktistov). \textit{Advances in Neural Information Processing Systems}, 2024.

@@

\textbf{Convex-Concave Interpolation and Application of PEP to the Bilinear-Coupled Saddle Point Problem} (Valery Krivchenko, Alexander Gasnikov, Dmitry Kovalev). \textit{Russian Journal of Nonlinear Dynamics}, 2024.

@@

\textbf{\href{https://proceedings.neurips.cc/paper/2019/hash/6a8018b3a00b69c008601b8becae392b-Abstract.html}{Stochastic proximal Langevin algorithm: Potential splitting and nonasymptotic rates}} (Adil Salim, Dmitry Kovalev, Peter Richtarik). \textit{Advances in Neural Information Processing Systems}, 2019.

@@

\textbf{\href{https://arxiv.org/abs/2503.12645}{Understanding Gradient Orthogonalization for Deep Learning via Non-Euclidean Trust-Region Optimization}} (Dmitry Kovalev). \textit{arXiv preprint arXiv:2503.12645}, 2025.
\textbf{\href{https://arxiv.org/abs/2503.06628}{On Solving Minimization and Min-Max Problems by First-Order Methods with Relative Error in Gradients}} (Artem Vasin, Valery Krivchenko, Dmitry Kovalev, Fedyor Stonyakin, Nazari Tupitsa, Pavel Dvurechensky, Mohammad Alkousa, Nikita Kornilov, Alexander Gasnikov). \textit{arXiv preprint arXiv:2503.06628}, 2025.

@@
